---
title: "p8105_hw1"
author: "Xiaohan Qiang"
date: "2026-09-25"
output: github_document
---
#problem1

```{r}
data("penguins", package = "palmerpenguins")
head(penguins)
library(ggplot2)
```
The penguins dataset contains `r nrow(penguins)` observations
and `r ncol(penguins)` variables.
The penguins dataset includes three penguin species:Adelie, Chinstrap and Gentoo. from three different island includes Biscoe, Dream and Torgersen.
Important variables include bill length (mm), bill depth(mm), flipper length(mm), body mass(g), sex, and year.
The mean flipper length is
`r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

```{r}
penguin_plot = ggplot(
  penguins,
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)
) +
  geom_point(na.rm = TRUE)

penguin_plot
```
Two observations with missing values in the plotting variables were excluded from the scatterplot.
```{r}
ggsave(
  filename = "penguins_scatterplot.png",
  plot = penguin_plot,
  width = 7,
  height = 5
)
```