---
title: "p8105_hw1"
author: "Xiaohan Qiang"
date: "2026-09-25"
output: github_document
---
#problem1

```{r}
data("penguins", package = "palmerpenguins")
head(penguins)
library(ggplot2)
```
The penguins dataset contains `r nrow(penguins)` observations
and `r ncol(penguins)` variables.
The penguins dataset includes three penguin species:Adelie, Chinstrap and Gentoo. from three different island includes Biscoe, Dream and Torgersen.
Important variables include bill length (mm), bill depth(mm), flipper length(mm), body mass(g), sex, and year.
The mean flipper length is
`r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

```{r}
penguin_plot = ggplot(
  penguins,
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)
) +
  geom_point(na.rm = TRUE)

penguin_plot
```
Two observations with missing values in the plotting variables were excluded from the scatterplot.
```{r}
ggsave(
  filename = "penguins_scatterplot.png",
  plot = penguin_plot,
  width = 7,
  height = 5
)
```

#problem2

```{r}
set.seed(123)

hw2_df = tibble::tibble(
  random_sample = rnorm(10),
  positive = random_sample > 0,
  character_vector = letters[1:10],
  factor_vector = factor(
    rep(c("low", "medium", "high"), length.out = 10)
  )
)

hw2_df
```
```{r}
mean(hw2_df$random_sample)
mean(hw2_df$positive)
mean(hw2_df$character_vector)
mean(hw2_df$factor_vector)
```
The mean of the numeric variable can be directly calculate. 
The mean of the logic variable means the proportion of TRUE value. That's because R treats TRUE as 1 and FALSE as 0 while calculate the mean value.
The character and factor variables return NA with warnings because their means are not defined.

```{r results='hide'}
as.numeric(hw2_df$positive)
as.numeric(hw2_df$character_vector)
as.numeric(hw2_df$factor_vector)
```
Converting the logical variable to numeric changes TRUE to 1 and FALSE to 0.
Converting the character variable to numeric produces NA values and a warning because its strings cannot be interpreted as numbers.
Converting the factor variable to numeric returns the integer codes of its levels rather than meaningful numerical values.
Therefore, numeric conversion does not necessarily make a variavle suitable for calculating a mean.